---
title: "San Francisco Tree Visualization"
output: html_notebook
---
Download the [dataset](https://data.sfgov.org/City-Infrastructure/Street-Tree-List/tkzw-k3nq/data) from SF Data and import into R. 

```{r}
library(readr)
Street_Tree_Map <- read_csv("C:/Users/Megan Stafford/Downloads/Street_Tree_Map.csv")
```

Select for three columns and take away missing location values.

```{r}
library(tidyverse)
nona <- select(Street_Tree_Map, Latitude, Longitude, qSpecies) %>%
  filter(Longitude != "")
```

Find the most common species and choose 8 of them to use in the map. 

```{r}

#t <- table(nona$qSpecies)
#t
by_species <- filter(nona, qSpecies %in% c("Tristaniopsis laurina :: Swamp Myrtle", "Prunus serrulata 'Kwanzan' :: Kwanzan Flowering Cherry", "Lophostemon confertus :: Brisbane Box", "Magnolia grandiflora :: Southern Magnolia", "Metrosideros excelsa :: New Zealand Xmas Tree","Pittosporum undulatum :: Victorian Box", "Platanus x hispanica :: Sycamore: London Plane", "Prunus cerasifera :: Cherry Plum"))

```
The top 8 values are: 
                      Tristaniopsis laurina :: Swamp Myrtle 
                                                                             6834
                      Prunus serrulata 'Kwanzan' :: Kwanzan Flowering Cherry 
                                                                             5679            
                      Lophostemon confertus :: Brisbane Box 
                                                                             8258
                      Magnolia grandiflora :: Southern Magnolia 
                                                                             6195
                      Metrosideros excelsa :: New Zealand Xmas Tree 
                                                                             8630                      
                     Pittosporum undulatum :: Victorian Box 
                                                                             6934
                     Platanus x hispanica :: Sycamore: London Plane 
                                                                            11356 
                     Prunus cerasifera :: Cherry Plum 
                                                                             6702
                                                                             

Create a dynamic map with plotly
```{r}
library(ggplot2)
library(ggmap)
qplot(Longitude, Latitude, data = by_species, color = qSpecies,
      xlab = NULL,
      ylab = NULL,
      labs(color = "Species of Tree")) 


```

There's an outlier shifting the graph lower. It needs to be filtered out. 

```{r}
no_outlier <- filter(by_species, Latitude >= 37.6)
qplot(Longitude, Latitude, data = no_outlier, colour = qSpecies, 
#      fill=factor(outcome,labels=c("low","high")
      maptype = "toner-background",
      xlab = NULL,
      ylab = NULL)
```

Now, using plotly:

```{r}
library(plotly)
qplot(Longitude, Latitude, data = no_outlier, colour = qSpecies, 
#      fill=factor(outcome,labels=c("low","high")
      maptype = "toner-background",
      xlab = NULL,
      ylab = NULL)%>%
  ggplotly()
```
